\sysfull

### 2018-04-17 paper/paging.tex
paging: remove stray alg caption
paging: fwd ref to API

%\begin{algorithm}[t]
\begin{wrapfigure}{t}{0.5\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{\texttt{PageFault}(tag $t$)}
	\caption{Two-phase commit}
	\label{algo:commit}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \Procedure{CommitPhase1}{} \Comment{On last coalesced task}
            \For {$i \in 0..|\texttt{working}|-1$}
                \State $t \gets \Call{Tag}{\texttt{working}[i]}$
                \State $\texttt{\underline{shadow}}[\Call{Tag}{\texttt{working}[i]}] \xleftarrow{\text{DMA}} \texttt{working}[i]$
                \State $\texttt{\underline{shadowList}}[\texttt{\underline{shadowCount}}] \gets t$
                \State $\texttt{\underline{shadowCount}} \gets \texttt{\underline{shadowCount}} + 1$
            \EndFor
            \State \Call{CommitPhase2}{}
        \EndProcedure
        \Procedure{CommitPhase2}{} \Comment{\texttt{\underline{commitIndex}} 0 on first boot}
            \State $\texttt{\underline{committing}} \gets \textbf{true}$
            \While{\texttt{\underline{commitIndex}} < \texttt{\underline{shadowCount}}}
                \State $t \gets \texttt{\underline{shadowList}}[\texttt{\underline{commitIndex}}]$
                \State \Call{commitToStore}{\texttt{\underline{shadow}}[t]}
                \State $\texttt{\underline{commitIndex}} \gets \texttt{\underline{commitIndex}} + 1$
            \EndWhile
            \State $\texttt{\underline{shadowCount}} \gets 0$
            \State $\texttt{\underline{commitIndex}} \gets 0$
            \State $\texttt{\underline{committing}} \gets \textbf{false}$
        \EndProcedure
        \Procedure{OnBoot}{} \Comment{Invoked on every boot}
            \If { \texttt{\underline{committing}} } \Call{CommitPhase2}{}
            \EndIf 
            \State $\texttt{\underline{shadowCount}} \gets 0$, $i_\text{victim} \gets 0$
        \EndProcedure
%	\end{algorithmic}
%\end{algorithm}
	\end{algorithmic}}}
\end{wrapfigure}

@@

\sys asks the programmer to use its {\tt RP} and {\tt WP} paging API methods on
every access to a protected variable.  These API invocations present a risk of
high overhead because there is a dynamic check on every read and write. An
alternative approach explored by prior work~\cite{alpaca} relied on a compiler
to analyze memory operations and try to insert memory
protection code mostly at the beginning of a task, leaving most memory accesses uninstrumented.

Despite the risk of per-access overhead, \sys's dynamic memory protection
scheme brings several benefits over a static approach.  First, the limitations
of static analysis preclude some uses of pointers due to potential pointer
aliasing. For example, in the presence of arbitrary pointer operation, a
function call using a function pointer, or an interrupt within a task, the
system cannot statically analyze the memory behavior.   Second, a static approach
cannot handle task coalescing because a protected variable's lifetime (i.e., from first use to commit) is unknown 
at compile time. \sys's dynamic, per-access instrumentation supports arbitrary use of pointers 
and enables task coalescing.
%
%Moreover, if the programmer wants to optimize for high performance, it is possible for the
%programmer to place {\tt RP} and {\tt WP} only minimally by carefully examining the code.
%We argue that the

>>>>

%\begin{algorithm}[t]
\begin{wrapfigure}{t}{0.5\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Two-phase commit}
	%\caption{Two-phase commit}
	\label{algo:commit}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \Procedure{CommitPhase1}{} \Comment{On last coalesced task}
            \For {$i \in 0..|\texttt{working}|-1$}
                \State $t \gets \Call{Tag}{\texttt{working}[i]}$
                \State $\texttt{\underline{shadow}}[\Call{Tag}{\texttt{working}[i]}] \xleftarrow{\text{DMA}} \texttt{working}[i]$
                \State $\texttt{\underline{shadowList}}[\texttt{\underline{shadowCount}}] \gets t$
                \State $\texttt{\underline{shadowCount}} \gets \texttt{\underline{shadowCount}} + 1$
            \EndFor
            \State \Call{CommitPhase2}{}
        \EndProcedure
        \Procedure{CommitPhase2}{} \Comment{\texttt{\underline{commitIndex}} 0 on first boot}
            \State $\texttt{\underline{committing}} \gets \textbf{true}$
            \While{\texttt{\underline{commitIndex}} < \texttt{\underline{shadowCount}}}
                \State $t \gets \texttt{\underline{shadowList}}[\texttt{\underline{commitIndex}}]$
                \State \Call{commitToStore}{\texttt{\underline{shadow}}[t]}
                \State $\texttt{\underline{commitIndex}} \gets \texttt{\underline{commitIndex}} + 1$
            \EndWhile
            \State $\texttt{\underline{shadowCount}} \gets 0$
            \State $\texttt{\underline{commitIndex}} \gets 0$
            \State $\texttt{\underline{committing}} \gets \textbf{false}$
        \EndProcedure
        \Procedure{OnBoot}{} \Comment{Invoked on every boot}
            \If { \texttt{\underline{committing}} } \Call{CommitPhase2}{}
            \EndIf 
            \State $\texttt{\underline{shadowCount}} \gets 0$, $i_\text{victim} \gets 0$
        \EndProcedure
%	\end{algorithmic}
%\end{algorithm}
	\end{algorithmic}}}
\end{wrapfigure}

@@

\sys asks the programmer to use its {\tt RP} and {\tt WP} paging API methods on
every access to a protected variable (cf. Section~\ref{sec:coala_api}).  These
API invocations present a risk of high overhead because there is a dynamic
check on every read and write. An alternative approach explored by prior
work~\cite{alpaca} relied on a compiler to analyze memory operations and try to
insert memory protection code mostly at the beginning of a task, leaving most
memory accesses uninstrumented.

Despite the risk of per-access overhead, \sys's dynamic memory protection
scheme brings several benefits over a static approach.  First, the limitations
of static analysis preclude some uses of pointers due to potential pointer
aliasing. For example, in the presence of arbitrary pointer operation, a
function call using a function pointer, or an interrupt within a task, the
system cannot statically analyze the memory behavior.   Second, a static approach
cannot handle task coalescing, because a protected variable's lifetime (i.e.,
from first use to commit) is unknown at compile time. \sys's dynamic,
per-access instrumentation supports arbitrary use of pointers and enables task
coalescing.
%
%Moreover, if the programmer wants to optimize for high performance, it is possible for the
%programmer to place {\tt RP} and {\tt WP} only minimally by carefully examining the code.
%We argue that the
